Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm

### 2023-06-28 paper/main.tex
添加了师兄的修改意见（v3.1）并修改（v3.2）

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{enumerate}
\usepackage{amsmath}
\DeclareMathOperator{\diag}{diag}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{bm}
\usepackage[ruled,linesnumbered]{algorithm2e}
\setcounter{MaxMatrixCols}{20}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
\def\T{\mathrm{T}}

@@

\begin{abstract}
    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
    In this paper, we propose a calculation method for the MAC of an RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
    By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
    The effectiveness of this method is validated on a novel and complex RBS structure.
    The results demonstrate the viability of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.

@@

The central principle of this method is to make the batteries in RBS connected in series as much as possible, thereby maximizing the output current of the RBS.
To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig.\ref{fig:main}.
Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in series.
Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.

@@

To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Fig.\ref{fig:isolated_mac}. 
Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}. 
This structure has two cases of isolating two batteries: 
one is to isolate two batteries within the same substructure (Fig.\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.\ref{fig:my-isolated-2w}), in which case $\eta=1$. 
From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.

Furthermore, the performance of output current for the three RBS when isolating batteries is also illustrated in Fig.\ref{fig:isolated_mac}. 
For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated. 
For Visairo's structure, the MAC decreases as the number of isolated battery cells increases, until $\eta=0$. 
In contrast, the MAC of the structure proposed in this work is positioned between the two structures. 
This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, which means a wider output current regulation range. 
On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control. 
In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{../attachments/isolated_mac.png}
    \caption{
        The variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al. , and the structure proposed in this paper.
    }\label{fig:isolated_mac}
\end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{enumerate}
\usepackage{amsmath}
\DeclareMathOperator{\diag}{diag}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{footnote}
\usepackage{bm}
\usepackage[ruled,linesnumbered]{algorithm2e}
\setcounter{MaxMatrixCols}{20}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
\def\T{\mathrm{T}}

@@

\begin{abstract}
    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
    In this paper, we propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
    By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
    The effectiveness of this method is validated on a novel and complex RBS structure.
    The results demonstrate the effectiveness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.

@@

The central principle of this method is to make the batteries in RBS connected in parallel as much as possible, thereby maximizing the output current of the RBS.
To universally and automatically achieve this, the overall process is divided into four steps, as shown in Fig.\ref{fig:main}.
Firstly, a directed graph model is established for subsequent computing, which not only contains the connected relationships between batteries and switches, but also retains the performance parameters of the batteries.
Subsequently, based on the equivalent circuit, the MAC problem is transformed into specific objective functions and constraints.
Then, the shortest paths (SPs, where additional batteries and switches on the path are penalized as distance) for the batteries are obtained using the Dijkstra algorithm to guide the batteries in the RBS connect in parallel.
Finally, a greedy algorithm is employed to organize the switches, allowing the batteries to connect via their SPs while satisfying the constraints, resulting in the MAC of the RBS.

@@

To illustrate this point, the MACs of the three RBS structures mentioned above are calculated after the batteries are isolated, as shown in Tab.\ref{tab:isolated_mac}. 
Specifically, for the structure presented in Fig.\ref{fig:study-stru-my}, the corresponding circuit states of MACs when isolating different numbers of batteries are depicted in Figs.\ref{fig:my-isolated-1}-\ref{fig:my-isolated-3}. 
This structure has two cases of isolating two batteries: 
one is to isolate two batteries within the same substructure (Fig.\ref{fig:my-isolated-2b}), in which case $\eta=2$; the other is to isolate one battery in each of the two substructures (Fig.\ref{fig:my-isolated-2w}), in which case $\eta=1$. 
From the results, it can be observed that the proposed method provides reasonable outcomes for isolating batteries with any number and position.

Furthermore, the performance of output current for the three RBS when isolating batteries is also shown in Tab.\ref{tab:isolated_mac}. 
For the structure proposed by Lawson et al., the MAC remains the same as that without isolated battery cells, i.e., $\eta=1$, when the number of isolated battery cells increases, until all the cells in the RBS are isolated. 
For Visairo's structure, the MAC decreases as the number of isolated battery cells increases, until $\eta=0$. 
In contrast, the MAC of the structure proposed in this work is positioned between the two structures. 
This indicates that the structure proposed in this paper, compared to Lawson's structure, has a larger MAC under the same number of batteries, which means a wider output current regulation range. 
On the other hand, by simply changing the states of $S_2$, $S_4$, $S_{11}$, and $S_{12}$ in the conversion structure, this structure can address the majority of battery isolation scenarios, whereas Visairo's structure requires specific battery targeting and switch control. 
In summary, the structure proposed in this paper has the advantages of both Lawson's and Visairo's structures.

\begin{table}[htbp]
  \centering
  \caption{
    The variation of MAC with the number of isolated batteries for different RBS structures, including the structure proposed by Lawson et al., Visairo et al. , and the structure proposed in this paper.
    }
    \label{tab:isolated_mac}
    \begin{tabular}{cccc}
    \toprule
    \multirow{2}[4]{*}{number of isolated batteries} & \multicolumn{3}{c}{$\eta$ of RBS structure} \\
\cmidrule{2-4}          & our  & Visairo's  & Lawson's  \\
    \midrule
    0     & 2     & 4     & 1 \\
    1     & 2     & 3     & 1 \\
    2     & 2$^{\rm a}$ or 1$^{\rm b}$ & 2     & 1 \\
    3     & 1     & 1     & 1 \\
    \bottomrule
    \end{tabular}
    \\
    \footnotesize{$^{\rm a}$ isolate two batteries within the same substructure, as shown in Fig.\ref{fig:my-isolated-2b}}\\
    \footnotesize{$^{\rm b}$ isolate one battery in each of the two substructures, as shown in Fig.\ref{fig:my-isolated-2w}}
\end{table}
